This section records only the critical-line exclusion target used in the main spine.
Detailed Stage~6 mechanism design (transfer templates, defect quantities, repair chains, and fallback routes) is moved to technical notes so that the main manuscript remains readable for audit.

\subsection*{Critical-line exclusion target (main theorem target)}
\begin{drafttheorem}[Target B: exclusion of admissible off-line balance]
\label{thm:stage6-master-exclusion-target}
\placeholder{Theorem target under construction; proof not yet provided.}
Let
\[
\mathcal{A}_{\mathrm{strip}}:=\{s\in\mathcal{A}:0<\RePart(s)<1\},
\qquad
\mathcal{B}:=\{s\in\mathcal{A}_{\mathrm{strip}}:\Phi_H(s)=0\}.
\]
Under one explicit synchronized hypothesis package $\mathcal{H}_{\mathrm{excl}}$, the argument attempts to prove
\[
\forall s\in\mathcal{B},\qquad \RePart(s)=\tfrac12.
\]
Equivalent set form:
\[
\mathcal{B}\cap\{s\in\mathcal{A}_{\mathrm{strip}}:\RePart(s)\neq\tfrac12\}=\varnothing.
\]
This theorem target is open in the current manuscript version.
\end{drafttheorem}

\subsection*{How this section interfaces with the RH reduction}
\begin{proposition}[Use of the exclusion target in the proof spine]
If \cref{thm:target-correspondence} and \cref{thm:stage6-master-exclusion-target} are both proved under compatible assumptions, then the RH reduction in \cref{prop:rh-reduction-main-spine} follows.
\end{proposition}

\begin{remark}[Audit boundary]
This section states the endpoint needed from the critical-line argument.
It does not claim that transfer-to-global closure, no-alternative-locus closure, or any specific contradiction mechanism has been proved.
Those remain open technical burdens documented outside the main proof spine.
\end{remark}
