This discussion section is interpretive.
It is not part of the formal proof itself.

\paragraph{Purpose of the current revision.}
The manuscript now presents one short proof spine in the main text:
(1) define balance, (2) state correspondence, (3) state critical-line exclusion, (4) derive RH conditionally.
This is a presentation decision for audit clarity.
It does not reduce the technical burden of the open steps.

\paragraph{What the framework attempts to show.}
The argument attempts to show that if the balance predicate is put in exact correspondence with nontrivial zeros, and if balanced points are proved to lie only on $\Re(s)=\tfrac12$, then RH follows.
The framework suggests a spectral-coherence route to those two targets, but those targets remain open in the current manuscript version.

\paragraph{Why the detailed machinery was demoted from the spine.}
Earlier drafts embedded transfer subtargets, neutralizing theorems, defect-function bookkeeping, and repair chains directly in the core narrative.
Those details are useful for technical development, but they obscured the primary logical structure.
In this revision, that machinery is treated as supporting technical material rather than core proof flow.

\paragraph{Current mathematical status.}
The manuscript remains a proposed proof framework under review.
The RH deduction in the main text is conditional on open theorem targets.
No claim of complete proof is made.

\paragraph{Interpretive boundary.}
Heuristic motivation, computational checks, and architectural planning can guide research, but they are not substitutes for theorem-level proofs.
Formal validity depends only on statements proved under explicit hypotheses.
