This section records the present limits of the argument in compact audit form.

\subsection*{Scope and standard}
The manuscript is a proposed proof framework.
Only theorem-level statements with explicit hypotheses count as proved content.
Heuristic and computational evidence remain supporting context.

\subsection*{Main open theorem burdens}
The simplified proof spine leaves two central open targets:
\begin{enumerate}
  \item \textbf{Target A (zero--balance correspondence).}
  A full theorem is still required to show exact correspondence between nontrivial zeros and balanced points.

  \item \textbf{Target B (critical-line exclusion for balanced points).}
  A full theorem is still required to show
  \(
  \mathcal{B}\subseteq\{s:\RePart(s)=\tfrac12\}
  \)
  on the declared admissible strip class.
\end{enumerate}

\subsection*{Technical dependencies remain open}
Although no longer expanded in the main spine, the following technical burdens remain unresolved and must eventually be discharged in supporting materials:
\begin{enumerate}
  \item operator-theoretic well-posedness and compatibility needed by the balance construction;
  \item analytic-control and continuation estimates needed to prevent hidden off-line balance branches;
  \item synchronization of assumptions across local arguments and strip-wide conclusions.
\end{enumerate}

\subsection*{Consequence for claims}
Because these burdens remain open, the manuscript does not claim a complete proof of RH.
It should be read as materials for mathematical audit of an argument that attempts to establish RH under explicit unresolved targets.
