This section presents a single proof spine for audit.
The manuscript keeps only the definitions and theorem targets needed for the RH reduction.
Detailed Stage~6 mechanisms are intentionally moved out of the main flow.

\subsection*{Established inputs (standard references)}
\begin{proposition}[Functional symmetry]
\label{prop:functional-symmetry}
The completed zeta function
\[
\xi(s)=\tfrac12 s(s-1)\pi^{-s/2}\Gamma\!\left(\tfrac{s}{2}\right)\zeta(s)
\]
satisfies $\xi(s)=\xi(1-s)$; see \cite{Riemann1859,Edwards1974,Titchmarsh1986}.
\end{proposition}

\begin{proposition}[Zero-set symmetries]
\label{prop:zero-symmetries}
If $\rho$ is a nontrivial zero of $\zeta$, then $1-\rho$ and $\overline{\rho}$ are also nontrivial zeros; see \cite{Edwards1974,Titchmarsh1986}.
\end{proposition}

\subsection*{Step 1: Balance predicate}
Fix an admissible class $\mathcal{A}$ and a balance functional $\Phi_H:\mathcal{A}\to\mathbb{C}$.
Define the balanced set in the strip by
\[
\mathcal{B}:=\{s\in\mathcal{A}_{\mathrm{strip}}:\Phi_H(s)=0\},
\qquad
\mathcal{A}_{\mathrm{strip}}:=\{s\in\mathcal{A}:0<\RePart(s)<1\}.
\]
The theorem targets below are always interpreted under one explicit synchronized hypothesis package, to be stated in full where those targets are eventually proved.

\subsection*{Step 2: Zero--balance correspondence target}
\begin{drafttheorem}[Target A: zero--balance correspondence]
\label{thm:target-correspondence}
\placeholder{Theorem target under construction; proof not yet provided.}
Under a fully specified admissibility and well-posedness package, the framework attempts to prove:
\[
\rho\text{ is a nontrivial zero of }\zeta
\quad\Longleftrightarrow\quad
\rho\in\mathcal{B}.
\]
This target is open in the current manuscript version.
\end{drafttheorem}

\subsection*{Step 3: Critical-line exclusion target}
\begin{drafttheorem}[Target B: exclusion of off-line balanced points]
\label{thm:target-uniqueness}
\placeholder{Theorem target under construction; proof not yet provided.}
Under a synchronized hypothesis package compatible with Target~A, the framework attempts to prove:
\[
\forall s\in\mathcal{B},\qquad \RePart(s)=\tfrac12.
\]
Equivalently,
\[
\mathcal{B}\cap\{s\in\mathcal{A}_{\mathrm{strip}}:\RePart(s)\neq\tfrac12\}=\varnothing.
\]
This target is open in the current manuscript version.
\end{drafttheorem}

\subsection*{Step 4: RH reduction}
\begin{proposition}[Conditional RH reduction inside the framework]
\label{prop:rh-reduction-main-spine}
Assume Targets~A and~B are proved under one compatible hypothesis package.
Then every nontrivial zero $\rho$ of $\zeta$ satisfies $\RePart(\rho)=\tfrac12$.
\end{proposition}

\begin{proof}
By Target~A, each nontrivial zero $\rho$ belongs to $\mathcal{B}$.
By Target~B, every element of $\mathcal{B}$ lies on $\RePart(s)=\tfrac12$.
Hence $\RePart(\rho)=\tfrac12$ for every nontrivial zero $\rho$.
\end{proof}

\begin{remark}[Status discipline]
The main spine above is a conditional proof program.
In this manuscript version, Targets~A and~B remain open theorem targets.
Therefore the RH conclusion is not claimed as an established theorem here.
\end{remark}
