This section explains the reduced framework around one direct object.

\subsection*{Canonical object in the main text}
The main flow uses only
\[
\Phi(q):=\Gamma(q)(1-q)\zeta(q).
\]
Balance means $\Phi(q)=0$.
No operator/resolvent surrogate is used in the core theorem chain.

\subsection*{Why this simplification is used}
The manuscript under review is intended for mathematical audit.
A single explicit object makes dependencies visible:
\begin{enumerate}
  \item define $\Phi$,
  \item relate $\Phi(q)=0$ to nontrivial zeros,
  \item prove critical-line exclusion for balanced points.
\end{enumerate}
This avoids treating a large family of alternative $\Phi_H$ constructions in the proof spine.

\subsection*{Role of operator language (secondary only)}
Operator-based interpretations may still be useful as heuristic motivation or future support.
In this revision they are secondary material and do not define balance in the main text.
Any future operator realization must be presented as support for the fixed canonical object above, not as a replacement for it.

\subsection*{Open burdens attached to the simplified core}
The simplification does not close the main proof gaps.
The remaining open burdens are:
\begin{enumerate}
  \item proving the theorem-level correspondence between $\Phi(q)=0$ and nontrivial zeta zeros on the strip;
  \item proving the theorem-level exclusion
  \[
  \Phi(q)=0\ \Longrightarrow\ \RePart(q)=\tfrac12
  \]
  on the declared domain.
\end{enumerate}

\begin{remark}[Audit boundary]
This section is a scope statement.
It records what object the argument uses and what is still open.
It does not claim RH and does not claim that the open bridges are solved.
\end{remark}
